FictionEro - Affective Impact of Fiction

### 2025-09-01 analysis/analysis.qmd
updated analysis script
analysis not completed, just a draft

dfsub2 <- read.csv("https://raw.githubusercontent.com/RealityBending/FictionEro/refs/heads/main/study2/data/data_participants.csv")
df2 <- read.csv("https://raw.githubusercontent.com/RealityBending/FictionEro/refs/heads/main/study2/data/data.csv") |> 
  right_join(
    select(dfsub2, Participant, Mobile, starts_with(c("Feedback_","BAIT")), COPS_Frequency, SexualActivity,- Feedback_Text),
    by = "Participant"
    ) |> 
    datawizard::rescale(select= c("Arousal", "Enticing", "Valence"), range=c(0, 6), to=c(0,1)) |> 
  datawizard::rescale(select= c("Realness"), range=c(-3,3), to=c(0,1)) |>
  mutate(Condition = case_when(
    Condition == "Fiction" ~ "AI-Generated",
    Condition == "Reality" ~ "Photograph"
  )) |>
  mutate(Condition = fct_relevel(Condition, "Photograph", "AI-Generated"),
         Gender =  fct_relevel(Gender, "Male", "Female"),
         SexualOrientation = fct_relevel(SexualOrientation, "Heterosexual", "Homosexual", "Bisexual"),
         PornFrequency = as.numeric(as.factor(COPS_Frequency)),
         SexualActivity_num = as.numeric(as.factor(SexualActivity)),
         ConditionBelief = case_when(
           Condition == "Photograph" & Realness > 0.5 ~ "True",
           Condition == "AI-Generated" & Realness < 0.5 ~ "True",
           .default = "False",
         )) |>
  rename(AllRealConfidence = "Feedback_AllRealConfidence",
         AllFakeConfidence = "Feedback_AllFakeConfidence",
         Enjoyment = "Feedback_Enjoyment"
         )|>
  mutate(across(starts_with("Feedback_"), as.factor)) |>
  mutate(ConditionBelief = as.factor(ConditionBelief)) |>
  mutate(StimuliType = case_when(
    grepl("couple", Stimulus, ignore.case = TRUE) ~ "Couple",
    TRUE ~ "Individual")) |>
  mutate(StimuliType = fct_relevel(StimuliType, "Individual", "Couple"))
```

@@

*Note*. Models for study 1 only include the conditions which were relevant to the participants secual orientation (e.g., seeing images of men as a heterosexual woman).

@@

  # ---- Fixed effects table ----
  tbl <- parameters::parameters(model1) |>
    as.data.frame() |>
    select(-Effects, -Group, -Component, -df_error, -CI) |>
    gt() |>
    # tab_header(title = title_table, subtitle = subtitle_table) |>
    fmt_number(columns = c("Coefficient", "SE", "CI_low", "CI_high", "z", "p"), decimals = 2) |>
    cols_label(
      Parameter = "Predictor",
      Coefficient = "β",
      SE = "SE",
      CI_low = "CI (lower)",
      CI_high = "CI (upper)",
      z = "z-value",
      p = "p"
    ) |>
    cols_merge(columns = c("CI_low", "CI_high"), pattern = "{1}, {2}") |>
    cols_label(`CI_low` = "95% CI") |>
    tab_style(
      style = cell_text(weight = "bold"),
      locations = cells_column_labels(everything())
    ) |>
    opt_table_lines()

@@

@@

>>>>

dfsub2 <- read.csv("https://raw.githubusercontent.com/RealityBending/FictionEro/refs/heads/main/study2/data/data_participants.csv")
df2 <- read.csv("https://raw.githubusercontent.com/RealityBending/FictionEro/refs/heads/main/study2/data/data.csv") |> 
  right_join(
    select(dfsub2, Participant, Mobile, starts_with(c("Feedback_","BAIT")), COPS_Frequency, SexualActivity,- Feedback_Text),
    by = "Participant"
    ) |> 
    datawizard::rescale(select= c("Arousal", "Enticing", "Valence"), range=c(0, 6), to=c(0,1)) |> 
  datawizard::rescale(select= c("Realness"), range=c(-3,3), to=c(0,1)) |>
  mutate(Condition = case_when(
    Condition == "Fiction" ~ "AI-Generated",
    Condition == "Reality" ~ "Photograph"
  )) |>
  mutate(Condition = fct_relevel(Condition, "Photograph", "AI-Generated"),
         Gender =  fct_relevel(Gender, "Male", "Female"),
         SexualOrientation = fct_relevel(SexualOrientation, "Heterosexual", "Homosexual", "Bisexual"),
         PornFrequency = as.numeric(as.factor(COPS_Frequency)),
         SexualActivity_num = as.numeric(as.factor(SexualActivity)),
         ConditionBelief = case_when(
           Condition == "Photograph" & Realness > 0.5 ~ "True",
           Condition == "AI-Generated" & Realness < 0.5 ~ "True",
           .default = "False",
         )) |>
  rename(AllRealConfidence = "Feedback_AllRealConfidence",
         AllFakeConfidence = "Feedback_AllFakeConfidence",
         Enjoyment = "Feedback_Enjoyment",
         Item = Stimulus
         )|>
  mutate(across(starts_with("Feedback_"), as.factor)) |>
  mutate(ConditionBelief = as.factor(ConditionBelief)) |>
  mutate(StimuliType = case_when(
    grepl("couple", Item, ignore.case = TRUE) ~ "Couple",
    TRUE ~ "Individual")) |>
  mutate(StimuliType = fct_relevel(StimuliType, "Individual", "Couple"))
```

@@

*Note*. Models for study 1 only include the conditions which were relevant to the participants sexual orientation (e.g., seeing images of men as a heterosexual woman).

@@

  # ---- Fixed effects table ----
  tbl <- parameters::parameters(model1, effects = "fixed") |>
    as.data.frame() |>
    select(-Effects, -df_error, -CI) |>
    gt() |>
    # tab_header(title = title_table, subtitle = subtitle_table) |>
    fmt_number(columns = c("Coefficient", "SE", "CI_low", "CI_high", "z", "p"), decimals = 2) |>
    cols_label(
      Parameter = "Predictor",
      Coefficient = "β",
      SE = "SE",
      CI_low = "CI (lower)",
      CI_high = "CI (upper)",
      z = "z-value",
      p = "p"
    ) |>
    cols_merge(columns = c("CI_low", "CI_high"), pattern = "{1}, {2}") |>
    cols_label(`CI_low` = "95% CI") |>
    tab_style(
      style = cell_text(weight = "bold"),
      locations = cells_column_labels(everything())
    ) |>
    opt_table_lines()

@@

### Random Effects

#### Arousal
```{r}
table_dvour <- function(g) {
  performance::performance_dvour(g) |> 
    arrange(desc(D_vour)) |> 
    gt::gt() |> 
    gt::data_color("D_vour", palette = c("red", "red", "orange", "yellow", "green"), domain = c(0, 1)) |> 
    gt::fmt_auto()
}

a1 <- modelbased::estimate_grouplevel(arousal1)
table_dvour(a1)

a2 <- modelbased::estimate_grouplevel(arousal2)
table_dvour(a2)

@@

### Participant effects

```{r}
plot_grouplevel_effects <- function(model, outcome_name = NULL) {

  # Colors
  colors <- c("Participant" = "#9C27B0", "Item" = "#FF9800")

  # Plot
  p <- ggplot(model, aes(x = Median, y = Level)) +
    geom_pointrange(aes(xmin = CI_low, xmax = CI_high, color = Group), size = 0.3) +
    ggside::geom_xsidedensity(aes(group = Group, fill = Group), color = NA, alpha = 0.3) +
    scale_color_manual(values = colors) +
    scale_fill_manual(values = colors) +
    theme_minimal() +
    theme(
      axis.text.y = element_blank(),
      axis.ticks.y = element_blank(),
      axis.title.x = element_text(size = 12),
      axis.title.y = element_blank(),
      panel.grid.minor = element_blank(),
      panel.grid.major.y = element_blank(),
      legend.position = "bottom"
    ) +
    labs(
      x = ifelse(is.null(outcome_name), "Random intercept (participant/item)", paste0(outcome_name, " random intercept")),
      y = "",
      color = "Group",
      fill = "Group"
    )

  return(p)
}

plot_grouplevel_effects(a1, outcome_name = "Arousal")
